Visualizing the Geography of Genetic Variants

### 2016-07-16 paper.tex
changed some grammer in conclusions

We also envision a variety of future extensions to the GGV that would allow for further dissection of geographical structure in large-scale population genomic datasets. Providing an interactive means of browsing neighboring variant sites near a SNP of interest would offer a unique view into patterns of linkage disequilibrium around that focal SNP which would be widely relevant to medical geneticist conducting genome-wide association studies as well as population geneticists interested in signatures of selection. We imagine incorporating a chromosomal browser such as jbrowse or a visualization inspired by the UCSC Genome Browser within the GGV would be greatly utilized by researchers and educators a like.

>>>>

We also envision a variety of future extensions to the GGV that would allow for further dissection of geographical structure in large-scale population genomic datasets. Providing an interactive means of browsing neighboring variant sites near a SNP of interest would offer a unique view into patterns of linkage disequilibrium around that focal SNP. This feature would be relevant to both medical geneticist conducting genome-wide association studies with in inteterests in fine mapping as well as population geneticists interested in scanning the genome to detect signatures of positive selection. We imagine that incorporating a chromosomal browser such as jbrowse or a visualization inspired by the UCSC Genome Browser within the GGV would be greatly utilized by researchers and educators alike.
